\pkg{sdmTMB}: An \proglang{R} Package for Fast, Flexible, and User-Friendly Generalized Linear Mixed Effects Models with Spatial and Spatiotemporal Random Fields

### 2024-02-10 doc/paper-jss/sdmTMB-paper.Rnw
Account for delta versions

<<dog-update, results='hide', message=FALSE, warning=FALSE, echo=TRUE>>=
fit_dg <- update(fit_tw, family = delta_gamma(),
  spatiotemporal = list("off", "iid"))
fit_dl <- update(fit_dg, family = delta_lognormal())
fit_dpg <- update(fit_dg, family = delta_poisson_link_gamma())
fit_dpl <- update(fit_dg, family = delta_poisson_link_lognormal())
@

>>>>

<<check-version, results='hide', echo=FALSE, include=FALSE>>=
# delta_poisson_link_gamma() deprecated in favor of delta_gamma(type = "poisson-link")
new_deltas <- packageVersion("sdmTMB") > '0.4.2.9000'
@

<<dog-update, results='hide', message=FALSE, warning=FALSE, echo=new_deltas, eval=new_deltas, include=new_deltas>>=
fit_dg <- update(fit_tw, family = delta_gamma(),
  spatiotemporal = list("off", "iid"))
fit_dl <- update(fit_dg, family = delta_lognormal())
fit_dpg <- update(fit_dg, family = delta_gamma(type = "poisson-link"))
fit_dpl <- update(fit_dg, family = delta_lognormal(type = "poisson-link"))
@

<<dog-update-old, results='hide', message=FALSE, warning=FALSE, echo=!new_deltas, eval=!new_deltas, include=!new_deltas>>=
fit_dg <- update(fit_tw, family = delta_gamma(),
  spatiotemporal = list("off", "iid"))
fit_dl <- update(fit_dg, family = delta_lognormal())
fit_dpg <- update(fit_dg, family = delta_poisson_link_gamma())
fit_dpl <- update(fit_dg, family = delta_poisson_link_lognormal())
@
